---
title: "TidyTuesday Week 19"
author: "Madeline Greene"
date: "5/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggpubr)
library(cowplot)
library(magick)
villagers <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-05-05/villagers.csv')
```


```{r}
#filter female villagers
villagers %>% 
  group_by(personality,gender) %>%
  filter(gender == "female")%>%
  summarise(count=n()) ->female_villagers
#filter male villagers
villagers %>% 
  group_by(personality,gender) %>%
  filter(gender == "male")%>%
  summarise(count=n()) ->male_villagers


# Compute percentages
female_villagers$fraction <- female_villagers$count / sum(female_villagers$count)
# Compute the cumulative percentages (top of each rectangle)
female_villagers$ymax <- cumsum(female_villagers$fraction)
# Compute the bottom of each rectangle
female_villagers$ymin <- c(0, head(female_villagers$ymax, n=-1))
# Compute label position
female_villagers$labelPosition <- (female_villagers$ymax + female_villagers$ymin) / 2
# Compute a good label
female_villagers$label <- paste0(female_villagers$personality, "\n value: ", female_villagers$count)

# Make the plot for female
female_villagers %>%
ggplot(aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=personality)) +
  geom_rect() +
  geom_label( x=3.5, aes(y=labelPosition, label=label), size=5) +
  scale_fill_brewer(palette="RdPu") +
  coord_polar(theta="y") +
  xlim(c(2, 4)) +
  theme_void() +
  theme(legend.position = "none") -> p1



# Compute percentages
male_villagers$fraction <- male_villagers$count / sum(male_villagers$count)
# Compute the cumulative percentages (top of each rectangle)
male_villagers$ymax <- cumsum(male_villagers$fraction)
# Compute the bottom of each rectangle
male_villagers$ymin <- c(0, head(male_villagers$ymax, n=-1))
# Compute label position
male_villagers$labelPosition <- (male_villagers$ymax + male_villagers$ymin) / 2
# Compute a good label
male_villagers$label <- paste0(male_villagers$personality, "\n value: ", male_villagers$count)

# Make the plot for male
male_villagers %>%
ggplot(aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=personality)) +
  geom_rect() +
  geom_label( x=3.5, aes(y=labelPosition, label=label), size=5) +
  scale_fill_brewer(palette="GnBu") +
  coord_polar(theta="y") +
  xlim(c(2, 4)) +
  theme_void() +
  theme(legend.position = "none") -> p2


#patchwork wouldn't work, so used ggarrange
figure <- ggarrange(p1, p2, 
                    labels = c("Female", "Male"))

#read in transparant image, increased its image_resize for more clarity of image
img1 <- image_read("animal_crossing_cartoon.png") %>%
  image_resize("1000x1000")  

#drew in image, played around with sizing
ggdraw() +
  draw_plot(figure) +
  draw_image(img1,
             x = 0.02, 
             y = 0,
             width = 1, height = 0.2) -> final_plot


ggsave("tidytuesday_week19.png", final_plot, width = 7, height = 4.5)


```
I really enjoyed this tidytuesday because I love Animal Crossings. With this data, I used a new ggplot, geom_rect, as well as making the data into a "donut". I had a lot of fun playing around with this data and figuring out how to make it into a donut shape. I also practiced using ggarrange. I tried using patchwork to add the two plots together, however, the error kept saying that I couldn't add two ggplots together.
