---
title: "Tidy Tuesday Week 12"
author: "Madeline Greene"
date: "3/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(remotes)
remotes::install_github("clauswilke/colorblindr")
library(colorblindr)

office_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-17/office_ratings.csv')
```


```{r}
office_ratings %>%
  ggplot(aes(x = factor(season), y = imdb_rating, fill = factor(season))) +
  geom_violin(width = 0.2) +
  labs(x = "Season", y = "IMDb Rating") +
  theme(legend.position = "none") -> office_plot

cvd_grid(office_plot) -> cvd_office_plot

cvd_office_plot
```

This week I really wanted to practice violin plots. I have only tried them once before and I felt that this data was perfect to pracice a violin plot because it would show the distribution of the ratings as well as the density of that data. The wider the area, the more dense/more of the same ratings would be. In addition, for one of my class assignments, we can use the colorblindr package, so I wanted to practice that as well!! I love how it makes a grid with different colorblind versions. 