---
title: "TidyTuesday Week 16"
author: "Madeline Greene"
date: "4/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(jpeg)
library(grid)
library(cowplot)
library(magick)
polls <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-14/polls.csv')
rankings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-14/rankings.csv')


```


```{r}
img <- image_read("kanye_face.png") %>%
  image_resize("300x300")  


rankings %>%
   mutate(title = factor(title), 
         points=(as.numeric(points))) %>%
  filter(artist %in% c("Kanye West", "Kanye West ft. Pusha T", "Kanye West ft. Rihanna & Kid Cudi", "JAY-Z & Kanye West", "Kanye West ft. Syleena Johnson", "Kanye West ft. Jamie Foxx", "Kanye West ft. Bon Iver")) %>%
  select(title, artist, points ) %>%
  arrange(points) %>%
  mutate(id = seq(1,n())) ->rankingpoints
 
label_rank <- rankingpoints
number_of_bar <- nrow(label_rank)
label_rank$angle_calc <- 90-360 *(label_rank$id) / number_of_bar
label_rank$angle <- ifelse(label_rank$angle_calc < (-90), label_rank$angle_calc + 180, label_rank$angle_calc)
label_rank$title <- paste(label_rank$title, " (", label_rank$points,")", sep="")



ggplot(rankingpoints, aes(x = id, y = points)) +
  geom_col(fill = "black") +
  ylim(-80, 80) +
  coord_polar(start = 0) +
  geom_text(data = label_rank, aes(x = id, y = 80,
                                   label = title), color = "lavenderblush3", fontface = "bold",
            size = 2.4, angle = label_rank$angle) +
  theme_minimal() +
  theme(axis.text = element_blank(),
      axis.title = element_blank(),
      panel.grid = element_blank(),
      panel.background = element_rect(fill = "lavenderblush4"))+
  annotate(geom = "text", x = 0, y = -30, label = "Kanye West", color = "white", size = 7) +
  annotate(geom = "text", x = 0, y = -45, label = "Top 13 Songs", color = "white", size = 4) +
  annotate(geom = "text", x = 0, y = -55, label = "BBC Music", color = "white", size = 3) -> plot


## have to order plot first, them add image on top of the plot
ggdraw() +
  draw_plot(plot) +
  draw_image(img,
             x = 0.405, 
             y = 0.34,
             width = 0.2, height = 0.2) -> final_plot


ggsave("tidytuesday_week16.png", final_plot, width = 7, height = 7)

```


This week for TidyTuesday, I practiced A LOT of new skills. I introduced myself to the package cowplot and magick. I did struggle at first but with trial and error, was able to upload a png with transparency to be part of my plot. I also spent a lot of time learning and figuring out how to adjust the labels with specific angles because of the circular barplot. This was a lot of trial and error and research but found that if I renamed the angles, I would not be hardcoding, which made the trial and error process much easier.  I am very happy on how it came out!!




