---
title: "TidyTuesday Week 15"
author: "Madeline Greene"
date: "4/12/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(jpeg)
library(grid)
tdf_winners <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-07/tdf_winners.csv')
```


```{r}
#read in PNG of background image
jpeg::readJPEG("tour_france.jpg") -> tour_image

tdf_winners %>%
  #some years don't have data for time_overall
  drop_na(time_overall) -> tdf_edit 


ggplot(tdf_edit, aes(x = start_date, y = time_overall)) +
  #how I added the background to the graph, placed this first before the data so wouldn't cover the data
  annotation_custom(rasterGrob(tour_image,
                               width = unit(1,"npc"), 
                               height = unit(1,"npc")), 
                    -Inf, Inf, -Inf, Inf) +
  #made a thicker line so was able to see it properly
  geom_line(col = "lightgoldenrod1", lwd= 2) +
  #added title and subtitle to explain graph better
  labs(title = "Tour de France Cyclist Overall Time",
       subtitle = "Decreased overall times throughout the years of competition",
       x = "Start date of the Tour",
       y = "Overall Time to Complete Race (hours)") -> tour_final




                              
```
This week's Tidy Tuesday really helped me practice a lot of things. Firstly, I learned a new skill which was uploading an image to have as the background of the figure. I did struggle with this but it helped me practice my terminal skills by changing where the image was being found. In addition, I practiced using titles and subtitles like we did in our previous homework assignment. I do want to add that I know my figure is deemed "bad". This is because of the y axis values. It DOES NOT start at 0. I wanted to make a big emphasis on the drop of values and this would not be as drastic if I changed the values.
